BIP-Predictor

### 2025-08-08 Sweave/BIP_predictor.Rnw
up

hp_c<-HP_obj$hp_trend
plot(hp_c,main=paste("Two-sided HP(",lambda_HP,")",sep=""),axes=F,type="l",xlab="Lags",ylab="")
abline(h=0)
axis(1,at=c(1,11,21,L),labels=-1+c(1,11,21,L))
axis(2)
box()

>>>>

hp_c<-HP_obj$hp_trend
plot(hp_c,main=paste("(One-sided) HP-C",sep=""),axes=F,type="l",xlab="Lags",ylab="")
abline(h=0)
axis(1,at=c(1,11,21,L),labels=-1+c(1,11,21,L))
axis(2)
box()
